%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{mershon-two-column-resume}


\begin{document}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     LAST UPDATED DATE
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%\lastupdated
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     TITLE NAME
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	

	\namesection{Brooks}{Mershon}{ \urlstyle{same}\url{http://www.brooksmershon.com} \\ \urlstyle{same}\url{http://www.boulderpilot.com} \\
		\href{mailto:brooksmershon@gmail.com}{brooksmershon@gmail.com} | 720.933.1079
	}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     COLUMN ONE
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{minipage}[t]{0.33\textwidth} 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     EDUCATION
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Education} 
		
		\subsection{Duke University}
		
		\descript{BS in Computer Science}
		\location{May 2016 | Durham, NC}
		\location{Cum. GPA: 3.74 / 4.0}
		\location{Duke Cycling Team Member}
		
		\sectionsep
		
		\subsection{New York University}
		\descript{Writers in New York 2014}
		
		\sectionsep
		
		\subsection{Pennsbury High School}
		\descript{Valedictorian}
		\location{June 2012 | Fairless Hills, PA}

		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     LINKS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\sectionsep
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     SKILLS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Skills}
		
		\subsection{Aviation}
		4034486CFI \\
		Commercial Pilot {\footnotesize \textit{\textbf{(ASEL, GLIDER)}}} \\
		Flight Instructor {\footnotesize \textit{\textbf{(ASEL, GLIDER)}}} \\
		Instrument Airplane \\
		FAA 1st Class Medical \\
		Over 58 makes and models flown \\
		
		EAA 1271516 \\
		IAC 440213 \\
		
		\sectionsep
		\location{Hours:}
		TOTAL: 1442 \textbullet{} PIC: 1347 \\
		12-MONTHS: 505 \textbullet{} 90-DAYS: 112 \\
		ASEL (PIC): 839 \textbullet{} GLIDER (PIC): 501 \\
		TAILWHEEL: 591 \\
		CROSS COUNTRY (PIC): 251 \\
		INSTRUCTOR: 233 \\
		NIGHT (PIC): 64 \\
		SIMULATED INSTRUMENT: 53 \\
		ACTUAL INSTRUMENT: 1 \\
		MULTI: 5 \\
				
		\sectionsep
		\location{Aircraft Ownership:}
		
		Pitts S1S | Jul. 2020 – Present \\
		Cessna 150L | Feb. 2020 – Present \\
		Skybolt 540 | Oct. 2019 – Jul. 2020 \\
		RV-6 | Aug. 2018 – Oct. 2019 \\
		
		\sectionsep
					
		\subsection{Programming}
		TypeScript \textbullet{} JavaScript \textbullet{} D3 \\
		Git \textbullet{} Make \\
		HTML \textbullet{} CSS \textbullet{} \LaTeX \\
		\location{Familiar:}
		C++ \textbullet{} Python \textbullet{} Java \textbullet{} R \textbullet{} PostgreSQL \\
		Emscripten
		
		\sectionsep
				
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%
		%     COLUMN TWO
		%
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
	\end{minipage} 
	\hfill
	\begin{minipage}[t]{0.66\textwidth} 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     EXPERIENCE
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Experience}
		
		\runsubsection{Boulder Pilot, LLC}
		\descript{| Co-Owner and Pilot}
		\location{March 2020 - Present | Boulder, CO}
		\vspace{\topsep} % Hacky fix for awkward extra vertical space
		\begin{tightemize}
			\item Started an aircraft ferry services and transition training LLC with an emphasis on experimental aircraft, biplanes, and other demanding tailwheel aircraft with a Fedex Express and Air National Guard Pilot.
			\item Developed the website, branding, merchandizing, and billing practices for the Boulder Pilot brand.
			\item Long term contract test pilot for an Experimental Ryan ST replica. All new, CAD from the ground up, kitplane design being brought to market.
			\item Formed long term relationship for flight test, design consultation, marketing, video production, and technical documentation with Timber Tiger Aircraft.
		\end{tightemize}
		\sectionsep
		
		\runsubsection{Mile High Gliding}
		\descript{| Manager and Pilot}
		\location{January 2019 - Present | Boulder, CO}
		\begin{tightemize}
			\item Experienced commercial glider and tow pilot. Scenic glider rides, transition training, and primary flight instruction. Responsible for staff pilot training.
			\item Rebranding and implementing advertising and web presence under new ownership and merging with Journeys Aviation.
			\item Organizing restoration of existing gliders and acquisition of new aircraft.
			\item Overhauling facilities and modernizing scheduling and billing practices.
		\end{tightemize}
		\sectionsep
		
		\runsubsection{Trimble SketchUp}
		\descript{| Software Developer }
		\location{July 2016 - January 2019 | Boulder, CO}
		\begin{tightemize}
			\item Significant engineering and design involvement bringing SketchUp Web to the EDU market, including integrating online file saving with Google Drive.
			\item Focused on improving the look, feel, and usability of the SketchUp Web user interface, specifically the search for Commands.
			\item 90 percent front-end work, 10 percent core geometry engine work. 
			\item Won ``Best Presentation'' and ``Best Overall Hack'' at internal 2018 hackathon.
		\end{tightemize}
		\sectionsep
		
		\runsubsection{The Washington Post}
		\descript{| Graphics Intern }
		\location{June 2015 - August 2015 | Washington, D.C.}
		\begin{tightemize}
			\item Designed \href{https://github.com/bmershon/published-urls}{graphics} for print and online publication using Adobe Illustrator. \item Developed interactive graphics that were published online on subjects including baseball statistics, historical U.S. nuclear testing, and environmental conservation.
		\end{tightemize}
		\sectionsep
		
		\runsubsection{Duke University Press}
		\descript{| Books Editorial Intern}
		\location{Jan 2015 – May 2015 | Durham, NC}
		\sectionsep
		
		\runsubsection{Versal}
		\descript{| Software Engineering Intern}
		\location{May 2013 – Aug 2013 | San Francisco, CA}
		\begin{tightemize}
			\item Developed simulations related to optics, epidemiology, image processing, and geometry as the company launched.
		\end{tightemize}
		\sectionsep
		
	\end{minipage} 
\end{document}  \documentclass[]{article}